Improving success ratio of EDF when taking into account preemption costs in uniprocessor periodic systems

### 2014-01-06 paper-paedf/paper-paedf.tex
Moved other unrelated papers to root (don't worry everyone I know what I'm doing. maybe.)

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{charter}
\usepackage{listings}
\usepackage{color}
\usepackage{url}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{float}
\usepackage{theorem}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}
%\usepackage[section]{placeins}

\newtheorem{theorem}{Theorem}

@@

\title{Improving success ratio of EDF when taking into account the preemption cost in uniprocessor periodic systems}
\author{Thomas Chapeaux}
\date{Summer 2013}
%opening
\sloppy
\begin{document}
\maketitle

@@

        A task $\tau_i$ generates jobs, denoted as the tuple $j_{i,j} = (a_{i, j}, d_{i,j}, c_{i,j})$ where :
        \begin{itemize}
            \item $j = \{1,2,...\}$ is an unique identifier for the job within $\tau_i$.
            \item $a_{i,j} = O_i + (j-1) \cdot T_i$ is the arrival time (or \emph{activation time}) of the job.
            \item $d_{i,j} = a_{i,j} + D_i$ is an absolute deadline at which the job must be completed.
            \item $c_{i,j} = C_i$ is the time it takes to complete the job (\emph{execution time}).
        \end{itemize}
h
        We also assume a discrete time, meaning that we consider that time passes one unit (sometimes called \emph{clock tick}) at a time. This means that the values listed above must be integers and that jobs will execute for whole units.\\

@@

        A scheduling policy is said to be \textbf{idling} if it allows instants at which no jobs are executing even if there are active (i.e. released and unfinished) jobs present in the system. Such instants are then called \textbf{idled instants}. They are not to be confused with \emph{idle times}, another important concept in feasibility analysis which is not discussed here.\\

@@

        A system is said to be \textbf{schedulable by a scheduling policy} if it exists a scheduling policy such that every job in the task set completes before its deadline is reached. A system schedulable by at least one scheduling policy is said to be \textbf{feasible}.\\

@@

        For (a)synchronous constrained deadline systems, $[O_{max}, O_{max} + 2 \cdot H]$ (with $O_{max}$ being the maximal task offset and $H$ the LCM of periods) is a feasibility interval for EDF.

@@

        When scheduling this system with EDF, we see that at instant $O_{max} + 2 \cdot H$, the system has not reached a periodic behavior yet. This only happens at instant $O_{max} + 4 \cdot H$, as seen on Fig.~\ref{fig:edf_longtransitive}.\\

@@

        \subsubsection{Idling dominate non-idling}

@@

>>>>

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{charter}
\usepackage{listings}
\usepackage{color}
\usepackage{url}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{float}
% \usepackage{theorem}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}
%\usepackage[section]{placeins}

\newtheorem{theorem}{Theorem}
\newtheorem{lemme}{Lemme}

@@

\title{Improving success ratio of EDF when taking into account preemption costs in uniprocessor periodic systems}
\author{Thomas Chapeaux}
\date{Summer 2013}
%opening
\sloppy
\begin{document}
\maketitle

@@

        A task $\tau_i$ generates jobs, denoted as the tuple $j_{i,j} = (a_{i, j}, d_{i,j}, c_{i,j})$ where :
        \begin{itemize}
            \item $j = \{1,2,...\}$ is an unique identifier for the job within $\tau_i$.
            \item $a_{i,j} = O_i + (j-1) \cdot T_i$ is the arrival time (or \emph{activation time}) of the job.
            \item $d_{i,j} = a_{i,j} + D_i$ is an absolute deadline at which the job must be completed.
            \item $c_{i,j} = C_i$ is the time it takes to complete the job (\emph{execution time}).
        \end{itemize}

        We also assume a discrete time, meaning that we consider that time passes one unit (sometimes called \emph{clock tick}) at a time. This means that the values listed above must be integers and that jobs will execute for whole units.\\

@@

        A scheduling policy is said to be \textbf{idling} if it is not work-conserving, i.e. it allows instants at which no jobs are executing even when there are active jobs (i.e. released and unfinished) in the system. Such instants are then called \textbf{idled instants}. They are not to be confused with \emph{idle times}, another important concept in feasibility analysis which is not discussed here.\\

@@

        A system is said to be \textbf{schedulable} if it exists a scheduling policy such that every job in the task set completes before its deadline is reached. A system schedulable by at least one scheduling policy is said to be \textbf{feasible}.\\

@@

        For (a)synchronous constrained deadline systems, $U_{tot}$ is still a necesary condition, but is not sufficient. When that condition is fulfilled, $[O_{max}, O_{max} + 2 \cdot H]$ (with $O_{max}$ being the maximal task offset and $H$ the LCM of periods) is a feasibility interval for EDF.

@@

        When scheduling this system with EDF, we see that at instant $O_{max} + 2 \cdot H$, the system has not reached a periodic behavior yet even if $U_{tot} \leqslant 1$. Indeed, the periodic behavior begins at instant $O_{max} + 4 \cdot H$, as seen on Fig.~\ref{fig:edf_longtransitive}.\\

@@

        \subsubsection{Idling strictly dominates non-idling}

        Non-idling (or work-conserving) algorithms are a special case of idling algorithms. In the free preemption model, EDF was a non-idling optimal algorithm, which proved that the idling algorithms did not offer any advantage with regards to schedulability.

        \begin{lemme}
        With the costly preemption assumption, there are constrained deadline systems schedulable by an idling algorithm and not schedulable by any non-idling algorithm.
        \end{lemme}

        \begin{proof}
        Consider the following system

@@

        \end{proof}
